---
title: "vimr"
author: "LSHTM"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## vimr - Vaccine Impact Model
'vimr' is a vaccine impact model (R package) for estimating the health impact of vaccination programmes at the national level for a given set of countries. This R package is based of the spreadsheet-based tool (UNIVAC) which is a universal framework for evaluating vaccine policy options in low- and middle-income countries, and is accessible at https://www.paho.org/provac-toolkit/.


### Vaccine Impact Modelling using vimr
* Estimate the health impact of vaccination at the national level.
* Hib, pneumococcal and rotavirus vacccination can be separately analysed.
* Multiple countries can be analysed and vaccine impact estimates are generated for each country.

Please see below for examples of vaccine impact modelling for each of the vaccines.

### Hib vaccine 


### Pneumococcal vaccine


### Rotavirus vaccine


### Reference manual
Refer to the reference manual 'univacr.pdf' for information on the datasets and functions included in this package. 

```{r echo=T, eval=F}
# load package
library (vimr)

# list all datasets in this package
data (package="vimr")

# view documentation of a specific dataset 
# example: dataset for under 5 mortality rate
?data.u5mortality

# view a specific dataset
data.u5mortality

# view documentation for a specific function
# example: RunCohort function
?RunCohort

# view source code of a specific function
RunCohort

# list all datasets and functions included in this package
ls ("package:vimr")

# list vignettes included in this package 
vignette (package="vimr")


```





